\section{Summary}

We described the design, assembly, installation, and calibration of six new Pre-Shower Calorimeter (PCAL) modules
for CLAS12. The PCAL were built to extend the performance of the CLAS Electromagnetic Calorimeters (EC) for
operation using beam energies up to 12~GeV. Both PCAL and EC are sampling calorimeters utilizing a novel triangular
hodoscope geometry with a combination of stereo transverse and threefold longitudinal readout of electromagnetic
showers. The PCAL design extends the performance of the EC by increasing the total radiation length need to fully
absorb electron and photon showers.  In addition PCAL uses wave-shifting fiber readout to improve both absolute
scintillator light yield and light attenuation, while increasing the transverse segmentation improves the spatial
resolution by at least a factor of 2. Preliminary analysis of physics runs with 7.5 and 10.6~GeV electron beams
indicate the combined system of PCAL+EC meets the design goals for position, energy, and timing resolution as well
as electron trigger efficiency. The neutron detection efficiency shows the expected momentum dependence, although
the absolute efficiency does not yet reach the 80$\%$ expected from simulations. At present we are still in the early
stages of studying the luminosity and resolution dependence of the CLAS12 reconstruction efficiency.

\section*{Acknowledgments}

Thanks to F.-X.~Girod for the use of his preliminary analysis of $\pi^0$ energy corrections. Acknowledgments go to
T.~Chetry and N.~Compton of Ohio University for programming contributions towards defining the PCAL and EC
geometry and development of  calibration algorithms and to the Hall~B engineering and technical staff for their
careful attention to the design, transportation, and installation of the PCAL modules. This material is based upon
work supported by the U.S. Department of Energy, Office of Nuclear Physics Division, under contract No.
DE-AC05-06OR23177 and was also supported by the National Science Foundation Major Research Instrumentation
Project (MRI) grant PHY-0821173.





