\section{Overview}

A primary goal of the CLAS12 physics program is to make a systematic study of internal nucleon dynamics by
accessing the nucleon's Generalized Parton Distributions (GPDs). This is accomplished through measurements of
Deeply Virtual Compton Scattering (DVCS), Deeply Virtual Meson Production (DVMP), and single spin asymmetries
(SSA). These experiments require accurate kinematical analysis of neutral and charged particles at high momentum.
In particular, all CLAS12 electroproduction experiments require the efficient detection and reliable identification
of energetic electrons, photons, and neutrons using the forward electromagnetic calorimeter (ECAL).

For CLAS12 it was necessary to augment the existing CLAS calorimeter (EC)~\cite{clas6nim} with a separate
pre-shower calorimeter (PCAL) installed in front of the EC. Simulations using GEANT4~\cite{nim:sim} showed that the thickness
of the EC alone (16 radiation lengths) would not be sufficient to absorb the full energy of electromagnetic showers
produced by electrons and photons with momenta above 5~GeV. Since the ECAL is used in the trigger this would
ultimately reduce the efficiency for detection of the highest energy electrons. High energy neutral mesons
($\pi^{0}$,$\eta$) present a challenge as well. Neutral mesons decay immediately into two photons with an
opening angle that decreases as the momentum increases. This calls for an improved calorimeter position resolution, in order to resolve the two decay photons in the full momentum range of interest, up to few GeV.  This is particularly critical for the reconstruction
of the DVCS final state, since a single high energy photon is produced in the reaction $ep \to e'p'\gamma$ and the
largest background to this process is from single $\pi^{0}$ production, $ep \to e'p'\pi^{0}$. In addition, direct
$\pi^{0}$ production complements the DVCS measurements by accessing GPDs at low and high momentum transfer
$|t|$. Clearly, accurate and efficient $\pi^{0}$ reconstruction is crucial to separate these two processes. Finally, the capability to detect and identify neutral mesons from the two-photons decay is of particular importance for the CLAS12 meson spectroscopy program, since these states are part of many of the reactions of interest~\cite{MesonSpec}.

The performance requirements of the PCAL were therefore driven by two factors: 1) electromagnetic shower
containment within the ECAL volume at the full electron energies to preserve the desired energy resolution and
efficiency and 2) improved spatial resolution to cleanly separate multiple shower clusters.  




