\subsection{Electromagnetic Calorimeters}

The Electromagnetic Calorimeters (ECAL) of the CLAS12 Forward Detector downstream of the torus and the
FTOF are lead-scintillator strip sampling calorimeters used for the detection of electrons, photons, and
neutrons. A pre-shower calorimeter (PCAL) is positioned in front of the EC calorimeter, which consists of two
parts, EC-inner (ECIN) and EC-outer (ECOU)~\cite{ecal-nim}. The ECAL reconstruction service provides a fast
and efficient algorithm for grouping scintillator {\it strips} with {\it hits} into multiple {\it peaks} and {\it clusters}
within the three submodules, PCAL, ECIN, and ECOU, for each of the six ECAL modules, while leaving cluster
matching and particle identification to the Event Builder service. Within the ECAL service, these various elements
exist as objects with methods, structures, and data members designed for calibration, pattern recognition,
diagnostics, and serial output. For example the service applies run-dependent calibration corrections for conversion
of the raw ADC and TDC digitized data to energy and time, and also provides formatted output banks used by
external services.  Energy thresholds and cluster identification criteria can also be configured to optimize the
reconstruction efficiency, suppress backgrounds, and avoid false or duplicate clusters arising from fluctuations at
the fringes of the electromagnetic showers.

The cluster finding algorithm makes use of the unique geometry and stereo readout features of the ECAL. As
discussed in Ref.~\cite{ecal-nim}, each triangular scintillator layer in the ECAL lead:scintillator sandwich is
transversely divided into strips, with the shortest strip at the corners. The slice direction rotates by 120$^\circ$
for each successive layer, providing three {\it views} labeled $U$, $V$, and $W$.  For each strip within a view,
layers are optically ganged together into a stack.  Individual photomultiplier tube (PMT) readout of each PCAL,
ECIN, and ECOU stack provides a pulse proportional to the summed energy deposited in the stack.

The algorithm begins by finding collections of contiguous strips having signals above a user-defined threshold for
each of the three views. These groupings are called {\it peaks} and their member strips are referred to as
{\it hits}.  Peak objects may be further subdivided based on the hit energy profile of the groupings. Each peak
object is associated with one or more stacks of strips that belong to it, and the three-dimensional geometry of each
stack is stored along with the peak data. The service uses this geometry data to determine which collection of
peaks belong to {\it clusters}.

\subsubsection {Cluster Position}

The criterion for defining a cluster requires the spatial intersection of three peaks, one from each of the $U$,
$V$, and $W$ views. Candidate peaks for a cluster search are based on a user-defined threshold for the
summed peak raw energy. Each peak is represented geometrically as a directed line segment determined by the
energy-weighted average of the mid-lines of each member strip. The degree of intersection of each $U$, $V$,
and $W$ peak triplet is determined by calculating the line of closest distance between a $U$ and $V$ peakline,
followed by the line of closest distance between the midpoint of the $UV$ line and the $W$ peakline. A
user-defined cut on this final $UV$-$W$ distance identifies the cluster, and the midpoint of the $UV$-$W$
line defines the transverse $(x',y')$ coordinates of the cluster in the local coordinate frame (with the $z'$
axis perpendicular to the ECAL planes. The longitudinal coordinate $z'$ is set to coincide with the layer of
maximum energy deposition to minimize parallax effects for tracks that are not normal to the detector surface
\cite{ecal-nim}. As the cluster reconstruction is performed before the matching with the other CLAS12
detectors that can provide particle identification, the same algorithm is applied to clusters originating from
charged or neutral particles.

\subsubsection {Cluster Energy}

Once the cluster is localized, the path from the cluster position to the PMT readout end is calculated for each $U$,
$V$, $W$ peakline and the peak energies are corrected for scintillator light attenuation.  For isolated clusters
the cluster energy is then defined as the sum of the corrected energy from each of the $U$, $V$, and $W$ peaks
that define the cluster.

More complicated scenarios arise from the triangular geometry of the ECAL hodoscope, which creates the
possibility of a single peak in the $U$, $V$, or $W$ view that shares the summed energy from two or more
clusters.  For these cases the energy in each cluster that shares that peak is assumed to be proportional to the
relative partial energies of the multiple clusters as measured in the other views.  For example, if there are two
clusters, both of which share the same $U$ peak, the summed energy $V+W$ is determined for each of the
clusters, and the ratio of these summed energies determines how much of the $U$ peak energy is assigned to
each of the two clusters.

Finally the clusters to be reported to external services are selected with a user-defined energy cut, and these
clusters are sorted according to energy. Typical software thresholds applied at the strip, peak, and cluster level
are 1, 3, and 10~MeV, respectively.

\subsubsection {Cluster Time}

Once the cluster is localized, the path from the cluster position to the PMT readout end is calculated for each
$U$, $V$, $W$ peakline and the peak timing is corrected for the propagation delay of the light, using the effective
velocity of light determined for each scintillator from the calibration procedure. For isolated clusters, the cluster
timing is then taken from the $U$, $V$, or $W$ peak with the largest uncorrected raw ADC value. This minimizes
the effect on the timing resolution from both the time-walk correction (i.e. the signal amplitude dependence of the
hit time) and the photoelectron statistical fluctuations.
